% --------------------------------------------------------------
% This is all preamble stuff
% --------------------------------------------------------------
 
\documentclass[12pt]{article}
 
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
\usepackage{enumitem}

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
 
\newenvironment{theorem}[2][Theorem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{lemma}[2][Lemma]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{exercise}[2][Exercise]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{question}[2][Question]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{corollary}[2][Corollary]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\newenvironment{solution}{\begin{proof}[Solution]}{\end{proof}}
 
\begin{document}
 
% --------------------------------------------------------------
%                         Start here
% --------------------------------------------------------------
 
\title{\textbf{CDT505 Project Management: Concepts and Tools}}%标题
\author{
\textbf{Quality control in pharmaceutical development}\\ \\\textbf{Jianlin Wang 3220869}\\
}%作者+加粗
\date{\today}%日期,今天

\maketitle%用于创建文档标题

\newpage%新建页面

\section{introduction}%章节
\subsection{Brief overview of the topic from the point of project management.}%副章节
Firstly,in this way%正文

\subsection{Importance of the topic and objective of your work.}
\indent ok %缩进但此处未生效 

\subsection{My plans on the topic or case study.}
abouts

\section{Literature Review}
\subsection{Summary of existing research related to the topic.}
about
\subsection{References to at least 5 reliable sources.}
12345
\subsection{Proper citation of sources.}
ok 
\section{Analysis and Discussion}
\subsection{Detailed analysis of the topic or case study. Relate your analysis to project
management principles.}
about
\subsection{Real-life examples or case studies. Include diagrams, tables, or charts if they
help illustrate your points.}
about
\subsection{Discussion on the findings.}
about

\section{Conclusion}













\newpage%强制创建新页面



\begin{enumerate} %有序
\item But Damn we Try!
\end{enumerate}





% -------------------------------------------------------------- 
\end{document}

\begin{itemize}%无序
  \item about
\end{itemize}